Intrinsic alignments from projected tidal fields: non-linear impact on cosmic shear probes

### 2024-06-21 sections/3_ia_models.tex
Updates from Overleaf

For minor adjustments, Eq. (\ref{eq:tidal_th_deltaNLA}) can be applied to alter the effective value of $b_{\rm TA}$. This allows for the recalibration of the intrinsic alignment contribution from an original bias value, $b_{\rm TA}^{\rm orig}$, to a new desired bias, $b_{\rm TA}^{\rm new}$, as:
%\begin{eqnarray}
%{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA}^{\rm new}}  = \frac{(1 + b_{\rm TA}^{\rm new} \delta)}{(1 + b_{\rm TA}^{\rm orig}\delta)}{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA}^{\rm orig}} \, .
%\label{eq:bta_rescale}
%\end{eqnarray}
\begin{eqnarray}
{\boldsymbol \epsilon}^{\rm new} = \frac{1 + \delta \: b_{\rm TA}^{\rm new}}{1 + \delta \: b_{\rm TA}^{\rm orig}}{\boldsymbol \epsilon}^{\rm orig} \, .
\label{eq:bta_rescale}
\end{eqnarray}
This has imitations in tits accuracy, but we will show later that it can nevertheless be applied to modify existing $\delta$-NLA mock data and yields good approximate solutions.

>>>>

For minor adjustments, Eq. (\ref{eq:tidal_th_deltaNLA}) can be applied to alter the effective value of $b_{\rm TA}$. This allows for the recalibration of the intrinsic alignment contribution from an original bias value, $b_{\rm TA}^{\rm orig}$, to a new desired bias, $b_{\rm TA}^{\rm new}$, as:
%\begin{eqnarray}
%{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA}^{\rm new}}  = \frac{(1 + b_{\rm TA}^{\rm new} \delta)}{(1 + b_{\rm TA}^{\rm orig}\delta)}{\boldsymbol \epsilon}^{\rm int}_{b_{\rm TA}^{\rm orig}} \, .
%\label{eq:bta_rescale}
%\end{eqnarray}
\begin{eqnarray}
{\boldsymbol \epsilon}^{\rm new} = \frac{1 + \delta \: b_{\rm TA}^{\rm new}}{1 + \delta \: b_{\rm TA}^{\rm orig}}{\boldsymbol \epsilon}^{\rm orig} \, .
\label{eq:bta_rescale}
\end{eqnarray}
This has limitations in its accuracy, but we will show later that it can nevertheless be applied to modify existing $\delta$-NLA mock data and yields good approximate solutions.

### 2024-06-21 sections/5_validation.tex
Updates from Overleaf

\subsection{Validation with full inference}
 \label{sec:inference}
\begin{figure}
%\includegraphics[width=\columnwidth]{graphs/triangle_nla_5D.pdf}
\includegraphics[width=\columnwidth]{graphs/triangle_bta_sweep.pdf}
\caption{Cosmological inference from the NLA-infused simulations, analysed the extended-NLA model. 
The cross-hairs represent the truth as fixed in the {\it Outer Rim} $N$-body simulations \citep{OuterRim}.}
\label{fig:triangle_nla}
\end{figure}
priors, {\sc CosmoSIS}, Takahashi $P(k)$, etc.

@@

\begin{figure}
%\includegraphics[width=\columnwidth]{graphs/triangle_nla_5D.pdf}
\includegraphics[width=\columnwidth]{graphs/TT_allsweep.pdf}
\caption{Cosmological inference from the TT-infused simulations, with all 3 IA params varied. The cross-hairs represent the truth as fixed in the {\it Outer Rim} $N$-body simulations \citep{OuterRim}.}
\label{fig:triangle_tt_all_ia_params}
\end{figure}

>>>>

\subsection{Validation with full inference}
 \label{sec:inference}
\begin{figure}
%\includegraphics[width=\columnwidth]{graphs/triangle_nla_5D.pdf}
\includegraphics[width=\columnwidth]{graphs/triangle_bta_sweep.pdf}
\caption{Cosmological inference from the NLA-infused simulations, analysed the extended-NLA model. 
The cross-hairs represent the truth as fixed in the {\it Outer Rim} $N$-body simulations \citep{OuterRim}. \niko{we should remove this fig, it is now irrelevant. or i can redo it with the new scale cuts}}
\label{fig:triangle_nla}
\end{figure}
priors, {\sc CosmoSIS}, Takahashi $P(k)$, etc.

@@

\begin{figure}
%\includegraphics[width=\columnwidth]{graphs/triangle_nla_5D.pdf}
\includegraphics[width=\columnwidth]{graphs/TT_allsweep.pdf}
\caption{Cosmological inference from the TT-infused simulations, with all 3 IA params varied. The cross-hairs represent the truth as fixed in the {\it Outer Rim} $N$-body simulations \citep{OuterRim}.\niko{we should remove this fig, it is now irrelevant. or i can redo it with the new scale cuts}}
\label{fig:triangle_tt_all_ia_params}
\end{figure}
